### 2016-07-13 2016_Proceedings_ISMIR/papers.tex
changed papers to be ordered strictly chronologically instead of by type (oral, poster)

\includepaper{WIMIR an Informetric Study on Women Authors in ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}

>>>>

\includepaper{WiMIR: An Informetric Study On Women Authors In ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}
